---
title: "Practical Machine Learning Course Project"
author: "bsneish"
date: "January 24, 2015"
output: html_document
---
Load libraries and dataset

```{r}
setwd("/Users/bn")
library(caret)
train<-read.csv("pml-training.csv")
test<-read.csv("pml-testing.csv")
```

remove columns from training set that we don't have any data for in the testing set (all NA)

```{r}
train2<-train[,colSums(is.na(test)) != nrow(test)]
```

remove row numbers and timestamp columns from training set

```{r}
train3<-train2[,c(2,6:60)]
```

train model using random forest, a robust classifier. this can take a while..

```{r}
modFit <- train(classe ~ .,method="rf",data=train3)
modFit$finalModel
```

OOB estimate of  error rate: 0.12%, which is good. very few errors in classification. will use to predict and produce submission files


```{r}
answers<-predict(modFit,newdata=test)


answers = rep("A", 20)

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

setwd("/Users/bn/test")
pml_write_files(answers)
```
